% MASTER'S THESIS IN MATHEMATICAL INFORMATION TECHNOLOGY
% Joel Lehtonen and Kristian Siljander
%
% Based on Timo Männikkö's template with some modifications made by
% Tuomo Sipola (M.Sc.).
%
% Uses latex template by Antti-Juhani Kaijanaho and Matthieu Weber.
%

\documentclass[finnish,logo,nonumbib,creativecommons,nocopyright,lof,pdftex,palatino,utf8]{gradu2}

%\usepackage[utf8]{inputenc}

\usepackage{palatino} % Better font
\usepackage[intlimits]{amsmath} % For better math mode, namely integrals
\usepackage{amssymb} % Math symbols

\usepackage[pdftex]{graphicx} % Pictures
\usepackage{pdfpages} % For inclusion of the article

\usepackage{hyperref}
\usepackage{cite}
\usepackage{framed}
\usepackage{verbatim} % Multi-line commenting.
\usepackage{rotating} % Vertical text used in temporary comments.
\usepackage{listings} % Source code


% Optional 1,5 point line spacing
%\usepackage{setspace}
%\onehalfspace

% Kirjastulostusta varten
\usepackage{scalefnt}

% Todo-tags help the examiner's work
\newcommand{\todo}[1]{\marginpar{\begin{framed}\begin{sideways}\textbf{TODO}: #1\end{sideways}\end{framed}}}

% Source code listings. Annotation can be done between [ and ] in Bash.
\lstset{frame=single,captionpos=b}
\renewcommand{\lstlistingname}{Listaus}
\lstdefinelanguage{bashshell}{language=bash,moredelim=[is][\itshape]{[[}{]]},morekeywords={mkdir,find,classifier,ls,parameter_analyzer,parameter2vector,xargs,apache2data},aboveskip=0.5cm}
\lstdefinelanguage{MyHaskell}{language=Haskell,morekeywords={ByteString,URL,UTCTime}}

% Define our own abbreviations list
\newenvironment{abbrlist}[1]{
  \begin{list}{}{\settowidth{\labelwidth}{\textbf{#1}}
  \setlength{\leftmargin}{\labelwidth}
  \addtolength{\leftmargin}{\labelsep}
  \renewcommand{\makelabel}[1]{\textbf{\hfill##1}}}}%
{\end{list}}

% No spacing with this enumeration
\newenvironment{enumerate_no_space}{
  \begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Remove pagebackref in the final version
% Add "pagebackref=true" to get page numbers where each reference is used
% Link version for internet viewing
%\usepackage[pdftex,colorlinks=true]{hyperref}

% PDF information tags
\pdfinfo{/Title (Web-palvelut ja niihin kohdistuvan poikkeavan tietoliikenteen
  analyysi käyttäen diffuusiokuvausmenetelmää) /Author (Joel Lehtonen ja Kristian Siljander) /Subject (Mitähän tähän pitäisi kirjoittaa?) /Keywords (tähän avainsana, toinen, jne.)}

%%% Actual content begins here

\title{Web-palvelut ja niihin kohdistuvan poikkeavan tietoliikenteen
  analyysi käyttäen diffuusiokuvausmenetelmää}
\translatedtitle{Web Services and Anomalous Web Traffic Detection Using Diffusion Maps}

\linja{Mobiilijärjestelmät}

\setauthor{Joel}{Lehtonen}
\setauthor{Kristian}{Siljander}
\yhteystiedot{joel.lehtonen@iki.fi}
\yhteystiedot{kristian.siljander@jyu.fi}
%\setdate{30}{8}{2008}
\license{Tämän teoksen käyttöoikeutta koskee Creative Commons
  Attribution-ShareAlike 3.0 Unported -lisenssi.}

%-miksi kiinnostavia
%-mitä tutkittiin
%-miten tutkittiin
%-tulokset

\abstract{ In recent years the popularity and usage of Web
  applications and services have grown rapidly and nowadays many of those
  services play an important role in our information society. Because
  of this, securing Web services is essential. The complexity of
  security attacks has renderd traditional security methods almost
  useless. Therefore new methods are being developed and diffusion
  maps are one of the most promising ones. In this thesis, the
  suitability of diffusion maps in evaluation of HTTP traffic is
  researched. The results show that the used methods are capable of
  detecting anomalous HTTP traffic from large data sets. Still, for
  active intrusion detection further research is needed. }

\tiivistelma{ Viime vuosina Web-sovellusten ja -palveluiden suosio on
  ollut voimakkaassa kasvussa, ja monet palveluista ovat nykyisin
  kriittisiä osia yhteiskuntamme toimivuuden kannalta.  Tämän johdosta
  palveluiden suojaaminen on noussut tärkeään roolin. Hyökkäysten myös
  muuttuessa yhä hienostuneimmiksi, eivät perinteiset
  tietoturvamenetelmät tarjoa enää riittävää suojaa. Tämän vuoksi
  uusia menelmiä kehitetään jatkuvasti. Diffuusiokuvaukset ovat yksi
  lupaavimmista menetelmistä, ja sen soveltuvuutta HTTP-liikenteen
  poikkeavuuksien havaitsemiseen tutkittiin tässä työssä. Saadut
  tulokset osoittivat, että menetelmää käyttäen pystytään havaitsemaan
  sellaiset HTTP-kyselyt, jotka eroavat tyypillisestä
  liikenteestä. Menetelmä vaatii kuitenkin jatkokehittelyä, jotta se
  soveltuisi tietoturvahyökkäysten rutiininomaiseen tunnistamiseen.}

\avainsanat{
anomalia,
diffuusiokuvaus,
N-gram -analyysi,
tietoturva,
Web-palvelu
}
\keywords{
anomaly,
data security,
diffusion maps,
N-gram analysis,
Web service
}

\def\termlistname{Lyhenteet}

\begin{document}

% Kirjastulostusta varten fontti luettavamman kokoiseksi
%\scalefont{1.18}

\include{sanasto}

\mainmatter

\include{johdanto}
\include{www-arkkitehtuuri}
\include{hyokkaykset}
\include{web-palvelut}
\include{web20}
\include{aiempi_tutkimus}
\include{tutkimusasetelma}
\include{tiedon_keruu}
\include{analysointi}
\include{johtopaatokset}

\bibliography{lahteet}{}
%\bibliographystyle{finplain}
\bibliographystyle{ieeetr}

\appendix

%\chapter{Published article}
%
%\includepdf[pages=-]{published_article.pdf}

\end{document}
